Scientific Reports Title to see here (20 words or less)

### 2016-08-18 sq_mobility/main.tex
ref

The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

@@

\bibliography{ref}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Figueredo:2009dg}. \cite{Figueredo:2009dg}

@@

%Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

>>>>

The Introduction section, of referenced text\cite{hawelka2014geo} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

@@

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{padmanabhan2014flumapper}.

@@

%Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
\bibliography{ref}
%\bibliographystyle{ref}
